Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2023-01-21 code/data-wrangling.qmd
erich wrangling

erich.whole$symptom.onset.interval <- as.period(erich.whole$symptom.onset.combined %--% erich.whole$ed.presentation.date.time)
erich.whole$time.to.ed.minutes <- time_length(erich.whole$symptom.onset.interval, unit = "minutes")
erich.whole$time.to.ed.hours <- time_length(erich.whole$symptom.onset.interval, unit = "hours")

>>>>

erich.whole$symptom.onset.interval <- as.period(erich.whole$symptom.onset.combined %--% erich.whole$ed.presentation.date.time)

erich.whole$time.to.ed.minutes <- time_length(erich.whole$symptom.onset.interval, unit = "minutes")

erich.whole$time.to.ed.hours <- time_length(erich.whole$symptom.onset.interval, unit = "hours")
